### 2021-04-15 manuscript.rmd
- added an interpretation of CI and CredI - Extended the conclusion

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China.

@@

# Contributions

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyse data from comparative content analyses. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.

>>>>

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China. While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of infference. The Bayesian approach alloows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling witin  0.18 and 0.33*. In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*. This example illustrates that a Bayesian approach allows us to interpret the results in a more intutitive way. On of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way (Morey et al., 2016).

@@

# Conclusion

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyse data from comparative content analyses. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Reserachers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative prios can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles. Still, eventually it worked and typical studies in comparative journalism research (HERE SOME EXAMPLES FROM THE LITERATURE) can be estimated in a reasonable time. (LETS TAKE A RANDOM SAMPLE OF 100 AND 1000 ARTICLES TO SHOW THIS IS NOT REALLY A PROBLEM).
